Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-02-27 2017-Xudong-SMT/OpenPNets-SMT.tex
OpenPNets-SMT.tex modified
Add some stuff into the 5th section.

\TODO{Xudong: Detailed description of the implementation}

@@

\TODO{Xudong: full result of the tool execution on the running example}

>>>>

\TODO{
Xudong: Detailed description of the implementation\\\\
5.1 Generation of the Open Transition\\\\
5.1.1 fresh variable\\\\
The variable in each SV are considered local, so does the variable of an open transition such as its hole behavior and its result action.
So we want rename them to make them unique, while we also hope them readable. The fresh variable has a confirmed format.
As pNets has a tree-like structure, we give every node of the pNets a tree index. And give them some counters to count the current times the SV, Hole or subnet is used, and the number of possible OT generated. \\\\
| format of fresh variable |\\\\
5.1.2 predicate generation\\\\
Combining, present all the possible working status of subnets. \\
Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.\\\\
5.1.3 assignment\\\\
Management of state variables.\\
Translating assignments into predicate terms.\\\\
5.2 Pruning the unsatisfiable results\\\\
Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
5.2.1 presentation\\\\
5.2.2 checking satisfiability\\\\
After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
}

@@

\TODO{
Xudong: full result of the tool execution on the running example\\\\
Open Automata of the CCS example.
}
